Rapid Processing and Georeferencing of Pushbroom Hyperspectral Imagery for Real Time Application by an Autonomous Aerial Vehicle

### 2023-09-30 paper/paper.tex
added more figures to paper

%=================================================================
% Full title of the paper (Capitalized)
\Title{Rapid Georeferencing n of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

@@

(**add a figure showing the different wavelength bands of publicly available satellites**)
\begin{figure}[H]
    \centering
    \includegraphics[width=12cm]{./assets/passbands.eps}
    \caption{Components of the Autonomous Drone HSI platform.}
    \label{fig:drone-components}
\end{figure}

@@

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Rapid Processing and Georeferencing of Pushbroom Hyperspectral Imagery for Real Time Application by an Autonomous Aerial Vehicle}
%\Title{A Procedure for the Rapid Processing and Georeferencing of Hyperspectral Imagery for Real-Time use by an Autonomous Aerial Vehicle}
% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=15cm]{./assets/passbands.eps}
    \caption{Relative spectral response for the wavelength passbands of the popular multi-spectral remote sensing sources Sentinel 2A, Sentinel 2B, Landsat 8, and MODIS. Data from the USGS}
    \label{fig:passbands}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=10.5 cm]{./figures/mNDWI_example.png}
\caption{Sample data product created on-board the aerial vehicle. The modified normalized difference water index is computed for each HSI and combined into a map. The plume of Rhodamine dye can clearly be seen in the water.\label{fig-map}}
\end{figure}
